---
title: Robust Fpop : A package to detect changepoints in the Presence of Outliers using the Biweight, L1 and Huber loss.
output: pdf_document
name: Guillem Rigaill
---

### Summary

Here we illustrate how use the robseg package implementing the 
the approach described in the following arXiv paper<cite>[1]</cite> available at : https://arxiv.org/abs/1609.07363.

### Install the package from github
You should first download the source code available at
https://github.com/guillemr/robust-fpop.
In R you can do this using the devtools package:

```{r install_package}
library(devtools)
install_github("guillemr/robust-fpop")
```


### Load the package

You can then load the package as follow and set some parameters for Rmd.

```{r load_the_package}
require(robseg)
knitr::opts_chunk$set(fig.width=11, fig.height=7) 
```

### Simulated data

In this Rmarkdown file we will illustrate the robseg function for the biweight, L1, Huber and L2 loss. 
As an example we will consider the simulation made in <cite>[2]</cite> using a student noise
rather than a Gaussian noise.

```{r simu_1}
source("Simulation.R")
i <- 1     ## there are 6 scenarios we take the first one
dfree <- 6 ## degree of freedom of the Student noise

## we recover the info of the first scenario
Ktrue   <- Simu[[i]]$Ktrue 
bkptrue <- as.integer( Simu[[i]]$bkpPage29[-c(1, Ktrue+1)] )
signaltrue <- Simu[[i]]$signal
sigmatrue  <- Simu[[i]]$sigma 

## we simulate one profile
set.seed(1)
x.data <- signaltrue + rt(n=length(signaltrue), df=dfree)*sigmatrue
```

We estimate the variance using successive differences and mad as follow:

```{r variance_estimation}
est.sd <- mad(diff(x.data)/sqrt(2))
```

In the following we illustrate how to run Robust Fpop for the Biweight, Huber, L1 and L2 losses.

### Robust Fpop with the Biweight loss

Here we ran Robust Fpop with the biweight loss.
We set the penalty to $\beta = 2\log(n)$ and the threshold parameter
to $K=3$. 

```{r Robust_Fpop_Biweight}
## run dynamic programming
res.ou <- Rob_seg.std(x = x.data/est.sd,  
                      loss = "Outlier", 
                      lambda = 2*log(length(x.data)), 
                      lthreshold=3)
## estimated changepoints 
cpt <- res.ou$t.est[-length(res.ou$t.est)]

## simple ploting of changes and smoothed profile
plot(x.data/est.sd, pch=20, col="black")
lines(res.ou$smt, col="red", lwd=2)
abline(v=cpt, lty=2, col="blue")

```


### Robust Fpop with the Huber loss

We now run Robust Fpop with the Huber loss fixing the penalty to $\beta=1.4\log(n)$ and the threshold parameter
to $1.345$.

```{r fpop_Huber}
## run dynamic programming
res.hu <- Rob_seg.std(x = x.data/est.sd,  
                      loss = "Huber", 
                      lambda = 1.4*log(length(x.data)), 
                      lthreshold = 1.345)
## estimated changepoints 
cpt <- res.hu$t.est[-length(res.hu$t.est)]

## simple ploting of changes and smoothed profile
plot(x.data/est.sd, pch=20, col="black")
lines(res.hu$smt, col="red", lwd=2)
abline(v=cpt, lty=2, col="blue")

```



### Robust Fpop with L1 loss
We now run Robust Fpop with L1 loss fixing the penalty to $\beta=\log(n)$.
In this example on segment is not detected : $[1556 - 1597]$.

```{r Robust_Fpop_L1}
## run dynamic programming
res.l1 <- Rob_seg.std(x = x.data/est.sd,  
                      loss = "L1", 
                      lambda = log(length(x.data)))

## estimated changepoints 
cpt <- res.l1$t.est[-length(res.l1$t.est)]

## simple ploting of changes and smoothed profile
plot(x.data/est.sd, pch=20, col="black")
lines(res.l1$smt, col="red", lwd=2)
abline(v=cpt, lty=2, col="blue")

```

### Fpop with the L2 loss
We now ran Fpop with the L2 loss <cite>[1]</cite> fixing
the penalty $\beta=2\log(n)$. In this example, some outlier data points are detected as segments.

```{r FPOP_L2}
## run dynamic programming
res.l2 <- Rob_seg.std(x = x.data/est.sd,  
                      loss = "L2", 
                      lambda=2*log(length(x.data)))

## estimated changepoints 
cpt <- res.l2$t.est[-length(res.l2$t.est)]

## simple ploting of changes and smoothed profile
plot(x.data/est.sd, pch=20, col="black")
lines(res.l2$smt, col="red", lwd=2)
abline(v=cpt, lty=2, col="blue")

```

### Some references

[1] Fearnhead, Paul and Rigaill, Guillem. "Changepoint Detection in the Presence of Outliers" arXiv:1609.07363

[2] Maidstone, Robert, et al. "On optimal multiple changepoint algorithms for large data." Statistics and Computing (2014): 1-15.)

