---
output: pdf_document
---
### Install the package

You should first download the source code available at
https://github.com/guillemr/robust-fpop.
Once this is done you can build and compile the package.
In command line on linux you can do this using:

R CMD build robseg

and then

R CMD INSTALL robseg_2016.10.19.tar.gz

### Load the package

You can then load the package as follow.

```{r load_the_package}
require(robseg)
```

### Simple examples

In this section we will illustrate the robseg function for the L2, biweight, L1 and Huber loss. As an example we will consider the simulation made in <cite>[1]</cite> using a student noise
rather than a Gaussian noise.

```{r simu_1}

source("Simulation.R")
i <- 1 ## there are 6 scenarios we take the first one
dfree <- 6 ## degree of freedom of the Student noise
## we recover the info of the first scenario
Ktrue <- Simu[[i]]$Ktrue 
bkptrue <- as.integer(Simu[[i]]$bkpPage29[-c(1, Ktrue+1)])
signaltrue <-  Simu[[i]]$signal
sigmatrue <- Simu[[i]]$sigma 

## we simulate one profile
set.seed(1)
x.data <- signaltrue + rt(n=length(signaltrue), df=dfree)*sigmatrue
```

We estimate the variance using MAD.
```{r variance_estimation}
est.sd <- varDiff(x.data)
```

### Fpop (L2)
We then run fpop with the L2 loss <cite>[1]</cite> fixing
the penalty ($\lambda$) to $\log(n)$. In this example, some outlier data points are detected as segments.

```{r fpop_L2}
## run dynamic programming
res.l2 <- fpop_intern(x.data/est.sd,  test.stat="Normal", pen.value=2*log(length(x.data)))

## same thing with changepoint package
res.l2_ <- cpt.mean(x.data/est.sd, penalty="Manual", pen.value=2*log(length(x.data)), method="PELT")
sum(res.l2$cpts != res.l2_@cpts)
## estimated changepoints 
cpt <- res.l2$cpts[-length(res.l2$cpts)]

## simple ploting of changes and smoothed profile
plot(x.data/est.sd, pch=20, col="black")
lines(res.l2$smt.signal, col="red", lwd=2)
abline(v=cpt, lty=2, col="blue")

```


### Robust Fpop (Huber)

We then run fpop with the Huber loss fixing the penalty to $1.4\log(n)$ and with a threshold parameter
of $1.345$.

```{r fpop_Huber}
## run dynamic programming
res.hu <- fpop_intern(x.data/est.sd,  test.stat="Huber", pen.value=1.4*log(length(x.data)), lthreshold=1.345)
res.hu_ <- Rob_seg.std(x.data/est.sd,  "Huber", lambda=1.4*log(length(x.data)), lthreshold=1.345)
sum(res.hu$cpts != res.hu_$t.est)

## estimated changepoints 
cpt <- res.hu$cpts[-length(res.hu$cpts)]

## simple ploting of changes and smoothed profile
plot(x.data/est.sd, pch=20, col="black")
lines(res.hu$smt.signal, col="red", lwd=2)
abline(v=cpt, lty=2, col="blue")

```

### Robust Fpop (Biweight)

To run fpop with the biweight loss fixing the penalty to $2\log(n)$ and with a threshold parameter
of $3$.

```{r fpop_Biweight}
## run dynamic programming
res.ou <- fpop_intern(x.data/est.sd,  test.stat="Outlier", pen.value=2*log(length(x.data)), lthreshold=3)
res.ou_ <- Rob_seg.std(x.data/est.sd,  "Outlier", lambda=2*log(length(x.data)), lthreshold=3)
sum(res.ou$cpts != res.ou_$t.est)
## estimated changepoints 
cpt <- res.ou$cpts[-length(res.ou$cpts)]

## simple ploting of changes and smoothed profile
plot(x.data/est.sd, pch=20, col="black")
lines(res.ou$smt.signal, col="red", lwd=2)
abline(v=cpt, lty=2, col="blue")

```

### Robust Fpop (L1)

We then run fpop with L1 loss fixing the penalty to $\log(n)$.
In this example on segment is not detected : [1556 - 1597].

```{r fpop_L1}
## run dynamic programming
res.l1 <- fpop_intern(x.data/est.sd,  test.stat="Laplace", pen.value=1*log(length(x.data)))
res.l1_ <- Rob_seg.std(x.data/est.sd,  "L1", lambda=1*log(length(x.data)))
sum(res.l1$cpts != res.l1_$t.est)
## estimated changepoints 
cpt <- res.l1$cpts[-length(res.l1$cpts)]

## simple ploting of changes and smoothed profile
plot(x.data/est.sd, pch=20, col="black")
lines(res.l1$smt.signal, col="red", lwd=2)
abline(v=cpt, lty=2, col="blue")

```

[1] Maidstone, Robert, et al. "On optimal multiple changepoint algorithms for large data." Statistics and Computing (2014): 1-15.)
